---
title: "The art of extensibility 1"
subtitle: "`tidy()` method"
description: "Writing statim extensions"
output: 
    rmarkdown::html_vignette:
        toc: true
vignette: |
    %\VignetteIndexEntry{The art of extensibility 1}
    %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
library(statim)
```

## Rationale

`{statim}` is so extendable, you can extend the existing methods or write your own and make it extensive. 

Here, I plan to extend `TTEST()` with another bootstrapping by simply adding another variation:

```{r}
add_variant(TTEST, x_by, "another_boot") %<-% variant(
    fn = function(.proc, .n = 1000L) {
        x = .proc$x_data[[1]]
        group_data = .proc$group_data
        
        grp = as.character(group_data[[1]])
        lvls = unique(grp)
        x1 = x[grp == lvls[[1]]]
        x2 = x[grp == lvls[[2]]]
        boot_fn = function(d, i) mean(d[i, 1]) - mean(d[i, 2])
        b = boot::boot(data.frame(x1, x2), boot_fn, R = .n)
        boot::boot.ci(b, type = "perc")
    }
)

another_boot_tt = 
    sleep |> 
    define_model(extra %by% group) |> 
    prepare_test(TTEST) |> 
    via("another_boot") |> 
    conclude()

another_boot_tt
```

`{statim}` has built-in output [S7 classes](https://joshuamarie.com/statim/reference/index.html#base-statistical-inference-output-class) support, which you can use them to register your own method into that specific class in order to be automatically processed into `{statim}` internals, like extracting your output in tibble format with `tidy()`. Otherwise, you must register them by your own. 

An example above doesn't register with one of built-in output S7 classes, so `tidy()` will fail. Fortunately, you can bring it down by using `making_tidy(<stat_fn>, <model_id / S7::class_formula>) %<-% method_tidy(...)`type of registry:

```{r}
making_tidy(TTEST, x_by) %<-% method_tidy(
    another_boot = function(.x, ...) {
        dat = .x@data
        tibble::tibble(
            R = dat$R, 
            t0 = dat$t0
        )
    }
)

another_boot_tt |> 
    tidy()
```

You can clean the `TTEST()` in `x_by` model pipeline slate by simply using `remove_variant()`. 

```{r}
remove_variant(TTEST, x_by, "another_boot")
```
